Titeln på avhandlingens språk

### 2022-08-30 model.tex
tweaking

We begin by discretizing normalized neuroticism into \emph{low} and \emph{high} ranges, \( [0.0, 0.5) \) and \( [0.5, 1.0) \) respectively. 
We also bin \ac{TTF} into terciles; we will refer to the first, second, and third terciles of \ac{TTF} as \emph{low}, \emph{medium}, and \emph{high impairment}.

@@

\begin{algorithm}
    \caption{Timing model algorithm}
    \KwIn{%
        \begin{itemize}
            \item $T_\text{start}$: start timestamp of the previous step.
            \item $T_\text{success}$: capture timestamp of the succesful sample of the previous step.
            \item $T_\text{end}$: end timestamp of the previous step.
            \item $t_\text{exec}$: execution time (in seconds) of the previous step.
        \end{itemize}%
    }
    \KwOut{$t_\text{exec}'$: execution time for the current step.}

    \Comment{%
        Initial values:\\
        $d \leftarrow 0$\\
        $I_\text{prev} \leftarrow \text{NULL}$
    }
    $t_\text{wait} \leftarrow T_\text{success} - (T_\text{start} + t_\text{exec})$\;
    $t_\text{round-trip} \leftarrow T_\text{end} - T_\text{success}$\;
    $i \leftarrow t_\text{wait} + t_\text{round-trip}$ \Comment*[r]{raw impairment}
    $I \leftarrow \text{BIN}(i)$ \Comment*[r]{bin impairment into\\discrete levels}

    \If{$I_\text{prev} == \text{NULL}$}{%
        $d \leftarrow 1$\;
        $T \leftarrow \text{NO TRANSITION}$\;
    } \ElseIf{$I_\text{prev} < I$}{%
        $d \leftarrow 1$\;
        $T \leftarrow \text{LOWER TO HIGHER} $
    } \ElseIf{$I_\text{prev} > I$}{%
        $d \leftarrow 1$\;
        $T \leftarrow \text{HIGHER TO LOWER} $  
    }

\end{algorithm}

>>>>

We begin by discretizing normalized neuroticism into \emph{low} and \emph{high} ranges, \( [0.0, 0.5) \) and \( [0.5, 1.0] \) respectively. 
We also bin \ac{TTF} into three ranges by splitting the data on the 3-quantiles; we will refer to these ranges of \ac{TTF} as \emph{low}, \emph{medium}, and \emph{high impairment}.

@@

% \begin{algorithm}
%     \caption{Timing model algorithm}
%     \KwIn{%
%         \begin{itemize}
%             \item $T_\text{start}$: start timestamp of the previous step.
%             \item $T_\text{success}$: capture timestamp of the succesful sample of the previous step.
%             \item $T_\text{end}$: end timestamp of the previous step.
%             \item $t_\text{exec}$: execution time (in seconds) of the previous step.
%         \end{itemize}%
%     }
%     \KwOut{$t_\text{exec}'$: execution time for the current step.}

%     \Comment{%
%         Initial values:\\
%         $d \leftarrow 0$\\
%         $I_\text{prev} \leftarrow \text{NULL}$
%     }
%     $t_\text{wait} \leftarrow T_\text{success} - (T_\text{start} + t_\text{exec})$\;
%     $t_\text{round-trip} \leftarrow T_\text{end} - T_\text{success}$\;
%     $i \leftarrow t_\text{wait} + t_\text{round-trip}$ \Comment*[r]{raw impairment}
%     $I \leftarrow \text{BIN}(i)$ \Comment*[r]{bin impairment into\\discrete levels}

%     \If{$I_\text{prev} == \text{NULL}$}{%
%         $d \leftarrow 1$\;
%         $T \leftarrow \text{NO TRANSITION}$\;
%     } \ElseIf{$I_\text{prev} < I$}{%
%         $d \leftarrow 1$\;
%         $T \leftarrow \text{LOWER TO HIGHER} $
%     } \ElseIf{$I_\text{prev} > I$}{%
%         $d \leftarrow 1$\;
%         $T \leftarrow \text{HIGHER TO LOWER} $  
%     }

% \end{algorithm}
